---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# occupationcross

<!-- badges: start -->
<!-- badges: end -->

The goal of occupationcross is to facilitate the application of crosswalks between occupational classifiers from different parts of the world.

## Installation

Install the development version of occupationcross from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Guidowe/occupationcross")
```
## Example

This is a basic example of how this package works :

Let´s load first *occupationcross*, and also *tidyverse*
```{r,warning=FALSE,message=FALSE}
library(occupationcross)
library(tidyverse)
```

Below is a sample from a database from USA - Current Population Survey, which contains a variable corresponding to the Census 2010 occupational code, named as *"OCC"*
```{r,warning=FALSE,message=FALSE}
toy_base_ipums_cps_2018
```
Applying the `census2010_to_isco08()` function we can obtain a reclassification of each case of our database into International Standard Classification of Occupations - 08 (ISCO-08) codes.
```{r,warning=FALSE,message=FALSE}
census2010_to_isco08(base = toy_base_ipums_cps_2018,
                     census = "OCC",
                     code_titles=TRUE)
```

