---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# occupationcross

<!-- badges: start -->
<!-- badges: end -->

The goal of occupationcross is to facilitate the application of crosswalks between occupational classifiers from different parts of the world.

## Installation

Install the development version of occupationcross from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Guidowe/occupationcross")
```
## Example

This is a basic example of how this package works :

Let´s load first *occupationcross*, and also *tidyverse*
```{r,warning=FALSE,message=FALSE}
library(occupationcross)
library(tidyverse)
```

The objects ```available_classifications``` and ```available_crosswalks``` show respectively which are the classifications collected and which crosswalks can be obtained applying the functions contained in this package.
```{r}
occupationcross::available_classifications
```

```{r}
occupationcross::available_crosswalks
```

Let´s use a sample database from a Mexico´s household survey (Encuesta Nacional de Ocupación y Empleo) already embedded in this package. This database contains a variable named *"p3"* corresponding to  SINCO 2011 (Sistema Nacional de Clasificación de Ocupaciones - 2011) occupational codes
```{r,warning=FALSE,message=FALSE}
toy_base_mexico
```

Applying the `sinco2011_to_isco08()` function we can obtain a reclassification of each case of our database into International Standard Classification of Occupations - 08 (ISCO-08) codes. The `code_titles` parameter allows you to get the occupation names both from the origin classification and isco 08 classification
```{r,warning=FALSE,message=FALSE}
crossed_base <- sinco2011_to_isco08(
  base = toy_base_mexico,
  sinco = p3,
  code_titles = TRUE)

crossed_base %>% 
  select(1,5:ncol(.))
```

