---
title: "Genre_analysis"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Genre_analysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

<!-- badges: start -->
<!-- badges: end -->

You can combine *occupationcross* with genre information available in households surveys. The package allows for international comparations on the genre distribution of occupations. Let's see a few examples usign the parameters ```add_major_groups``` and ```add_skill``` of our function ```reclassify_to_isco08```

## Installation

Install the development version of occupationcross from [GitHub](https://github.com/) with:

```{r,warning=FALSE,message=FALSE, results='hide'}
#devtools::install_github("Guidowe/occupationcross")
```

## Comparing ISCO-08 major groups and skill levels by genre in Argentina and the USA

Load first *occupationcross*, *tidyverse* and the package for the Argetinean households survey *eph*
```{r,warning=FALSE,message=FALSE}
library(occupationcross)
library(tidyverse)
library(ggthemes)
library(scales)
library(eph)
```

We get the dataframe from the individual version of the EPH survey (1st quarter 2018) and organize its labels using the *eph* package.

```{r,warning=FALSE,message=FALSE}
eph.2018.01.original <- get_microdata(year = 2018, 
                             trimester = 1, 
                             type='individual') %>% 
               organize_labels(., type='individual')
```

### ISCO-08 major groups

Using ```reclassify_to_isco08``` and setting ```add_major_groups``` as TRUE, we obtain the reclassification for the EPH's variable  *"PP04D_COD"*, which is originally clasified trough the national clasification system CNO2001.

```{r,warning=FALSE,message=FALSE}
eph.2018.01 <- reclassify_to_isco08(eph.2018.01.original, 
                                    PP04D_COD, 
                                    classif_origin="CNO2001", 
                                    add_major_groups = TRUE)
```

Now we can tabulate our new variable *"major_group"* using the EPH's variable for genre *"CH04"* and plot the results

```{r,warning=FALSE,message=FALSE}

genre_composition.arg<- eph.2018.01 %>% 
  filter(ESTADO==1 & !is.na(major_group)) %>% 
  mutate(genre= case_when(CH04==1 ~ "Male", 
                          CH04==2 ~ "Female")) %>% 
  group_by(major_group,genre) %>% 
  summarise (absolute=sum(PONDERA)) %>% 
  group_by(major_group) %>% 
  mutate(percentage= absolute/sum(absolute)) %>% 
  ungroup() %>% 
  mutate(major_group = str_wrap(major_group,width = 25))

ggplot(genre_composition.arg,
       aes(x = major_group,y = percentage,fill = genre))+
  geom_col()+
  labs(title = "Sex composition of employed persons by major groups",
       subtitle = "Argentina - 2018")+
  theme_minimal()+
  theme(axis.title = element_blank(),
        legend.title = element_blank())+
  scale_fill_hc()+
  scale_y_continuous(labels = scales::percent)+
  coord_flip()
```

The graph above shows the sex composition of each major group. The major group 1 (Managers) is unevenly distributed since 68% of people working at these occupations are men. This is the case also for occupations from major groups 8 and 7, related to shop-floor industrial activities, which are mostly done by men (87% and 90% respectivly).

Let's compare these results to the occupations distribution by sex in the USA. We shall use the IPUMS's version of the Current Population Survey 2018. If you want to reproduce this example, you should ask for the data extract of CPS at https://cps.ipums.org/ 

```{r,warning=FALSE,message=FALSE}

load("../data-raw/bases/cps2018_occ_genre.rda")
```


Once the dataframe is loaded, we can use  ```reclassify_to_isco08``` in order to reclassify the variable *"OCC"* that contains the occupation clasification with the *"Census2010"* system. We also set ```add_major_groups``` as TRUE.


```{r,warning=FALSE,message=FALSE}

cps.2018 <-  reclassify_to_isco08(cps2018_occ_genre, 
                                    OCC, 
                                    classif_origin="Census2010", 
                                    add_major_groups = TRUE)

```


Now we tabulate the data and plot it.

```{r,warning=FALSE,message=FALSE}
genre_composition.usa<- cps.2018 %>% 
  filter(EMPSTAT==10 & !is.na(major_group)) %>% 
  mutate(genre= case_when(SEX==1 ~ "Male", 
                          SEX==2 ~ "Female")) %>% 
  group_by(major_group,genre) %>% 
  summarise (absolute=n()) %>% 
  group_by(major_group) %>% 
  mutate(percentage= absolute/sum(absolute)) %>% 
  ungroup() %>% 
  mutate(major_group = str_wrap(major_group,width = 25))


ggplot(genre_composition.usa,
       aes(x = major_group,y = percentage,fill = genre))+
  geom_col()+
  labs(title = "Sex composition of employed persons by major groups",
       subtitle = "USA - 2018")+
  theme_minimal()+
  theme(axis.title = element_blank(),
        legend.title = element_blank())+
  scale_fill_hc()+
  scale_y_continuous(labels = scales::percent)+
  coord_flip()


```

The graph shows that occupations are unequaly distributed at major group 1 (Managers), whereas women represent 41% of total employmen and men 59%. The distribution is quite even for major groups 2 and 3. while women are the majority at major groups 4 and 5. In major groups 6 to 9, men are the majority

### Skill level analysis

Let's analyse the sex distribution of skill levels based on the 9 ISCO major groups. The param ```add_skill``` in the ```reclassify_to_isco08``` function will get the 3-tiers variable for skill level, indicating whether the job is high, medium or low skilled. First we get the variable *skill_level* for the two datasets we are using.


```{r,warning=FALSE,message=FALSE}
eph.2018.01 <- reclassify_to_isco08(eph.2018.01.original, 
                                    PP04D_COD, 
                                    classif_origin="CNO2001", 
                                    add_skill = TRUE)
                                    
cps.2018 <-  reclassify_to_isco08(cps2018_occ_genre, 
                                    OCC, 
                                    classif_origin="Census2010", 
                                    add_skill = TRUE)
```

Now we can tabulate the data and plot it to compare

```{r,warning=FALSE,message=FALSE}

genre_composition.skill.arg<- eph.2018.01 %>% 
  filter(ESTADO==1 & !is.na(skill_level)) %>% 
  mutate(genre= case_when(CH04==1 ~ "Male", 
                          CH04==2 ~ "Female")) %>% 
  group_by(skill_level,genre) %>% 
  summarise (absolute=sum(PONDERA)) %>% 
  group_by(skill_level) %>% 
  mutate(percentage= absolute/sum(absolute)) %>% 
  ungroup() %>% 
  mutate(skill_level = str_wrap(skill_level,width = 25))

genre_composition.skill.usa<- cps.2018 %>% 
  filter(EMPSTAT==10 & !is.na(skill_level)) %>% 
  mutate(genre= case_when(SEX==1 ~ "Male", 
                          SEX==2 ~ "Female")) %>% 
  group_by(skill_level,genre) %>% 
  summarise (absolute=n()) %>% 
  group_by(skill_level) %>% 
  mutate(percentage= absolute/sum(absolute)) %>% 
  ungroup() %>% 
  mutate(skill_level = str_wrap(skill_level,width = 25))

genre_composition.skill <- bind_rows("Argentina" = genre_composition.skill.arg, "USA"= genre_composition.skill.usa, .id="country")

ggplot(genre_composition.skill,
       aes(x = skill_level,y = percentage,fill = genre))+
  geom_col()+
  facet_wrap(. ~ country) +
  labs(title = "Sex composition of employed persons by skill level",
       subtitle = "USA - 2018")+
  theme_minimal()+
  theme(axis.title = element_blank(),
        legend.title = element_blank())+
  scale_fill_hc()+
  scale_y_continuous(labels = scales::percent)


```

In Argentina, High complexity occupations are perfomed 50-50 percent among women and men. In USA women are the majority at that level with 52%.

The package  *occupationcross* has thereby allowed us to carry out an international comparison based on different occupations classification systems. The same analysis that we have put forward for genre could be done using any of the socio-economic variables avaiable in datasets, such as age, region, incomes, etc.


