---
title: "Genre_analysis"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Genre_analysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

<!-- badges: start -->
<!-- badges: end -->

You can combine *occupationcross* with genre information available in households surveys. The package allows for international comparations on the genre distribution of occupations. Let's see a few examples for genre analysis usign the parameters ```add_major_groups``` and ```add_skill``` of our function ```reclassify_to_isco08```

## Installation

Install the development version of occupationcross from [GitHub](https://github.com/) with:

```{r,warning=FALSE,message=FALSE, results='hide'}
#devtools::install_github("Guidowe/occupationcross")
```

## Comparing ISCO-08 major groups by genre in Argentina

Load first *occupationcross*, *tidyverse* and the package for the Argetinean household survey *eph*
```{r,warning=FALSE,message=FALSE}
library(occupationcross)
library(tidyverse)
library(ggthemes)
library(scales)
library(eph)
```

We get the dataframe from the individual version of the survey for the 1st quarter 2018 and organize its labels using the *eph* package.

```{r,warning=FALSE,message=FALSE}
eph.2018.01 <- get_microdata(year = 2018, 
                             trimester = 1, 
                             type='individual') %>% 
               organize_labels(., type='individual')
```

Using ```reclassify_to_isco08``` and setting ```add_major_groups``` as TRUE, we obtain the reclassification for the EPH's variable  *"PP04D_COD"*, which is originally clasified trugh the national clasification system CNO2001.

```{r,warning=FALSE,message=FALSE}
eph.2018.01 <- reclassify_to_isco08(eph.2018.01, 
                                    PP04D_COD, 
                                    classif_origin="CNO2001", 
                                    add_major_groups = TRUE)
```

Now we can tabulate our new variable *"major_group"* using the EPH's variable for genre *"CH04"*

```{r,warning=FALSE,message=FALSE}

genre_composition<- eph.2018.01 %>% 
  filter(ESTADO==1 & !is.na(major_group)) %>% 
  mutate(genre= case_when(CH04==1 ~ "Male", 
                          CH04==2 ~ "Female")) %>% 
  group_by(major_group,genre) %>% 
  summarise (absolute=sum(PONDERA)) %>% 
  group_by(major_group) %>% 
  mutate(percentage= absolute/sum(absolute)) %>% 
  ungroup() %>% 
  mutate(major_group = str_wrap(major_group,width = 25))



ggplot(genre_composition,
       aes(x = major_group,y = percentage,fill = genre))+
  geom_col()+
  labs(title = "Sex composition of employed persons by major groups",
       subtitle = "Argentina - 2018")+
  theme_minimal()+
  theme(axis.title = element_blank(),
        legend.title = element_blank())+
  scale_fill_hc()+
  scale_y_continuous(labels = scales::percent)+
  coord_flip()
```



