---
title: "Ejemplo de uso de occupationcross"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Ejemplo de uso}
  %\VignetteEngine{rmarkdown::render}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(occupationcross)
```

`occupationcross` package provides some functions to apply crosswalks between different occupational clasiffications around the world.

## Installation


To install development version:

```{r, eval=FALSE, message=FALSE, warning=FALSE, include=TRUE}
# install.packages('devtools') si no tiene instalado devtools

devtools::install_github("Guidowe/occupationcross")
```


## WorkFlow Example: 
Lets read a household survey database that has occupations codified in Census 2010 codes. In our example we will use IPUMS database from   Current Population Survey (CPS-United States).          

We will take our `census2010_to_isco08()`function to aplly crosswalk to ISCO 08 codes.  

### Load libraries: 

```{r message=FALSE, warning=FALSE}
library(occupationcross)
library(dplyr)
library(tidyr)
```

### Load database:
Besides from USA CPS database we will read a Italy´s database from Labour Force Survey (LFS), which is allready codified in ISCO-08 codes

```{r}
usa_cps_base <- readRDS("../data-raw/bases/Base_USA2018.RDS")
italy_lfs_base <- readRDS("../data-raw/bases/IT2014.RDS")
```

### Apply crosswalk to ISCO 08 codes: `census2010_to_isco08()`
Our function requieres three basic arguments :

- `base`: Dataframe containing a variable with Census 2010 codes
- `census`: character indicating the variable name containing Census 2010 codes. In our case, in IPUMS-CPS database it is named "OCC"
- `summary`: logical indicating if you want a summary table counting case from each census2010 code to eacho isco08 code.
- `code_titles`: logical indicating if you want occupational titles besides codes.
```{r message=FALSE, warning=FALSE}
usa_cps_base_crossed <- census2010_to_isco08(base = usa_cps_base,census = "OCC",summary = FALSE,code_titles = T)
```

```{r}
ncol(usa_cps_base)
ncol(usa_cps_base_crossed)
```

The resulting dataframe *_usa_cps_base_crossed* has now three more variables provinding ISCO 08 codes, ISCO 08 titles and SOC 2010 codes (which was used to make an intermediate crosswalk).

Let´s see which are the most frecuent occupation in USA-CPS
```{r message=FALSE, warning=FALSE}
 usa_cps_base_crossed %>% 
  filter(!is.na(ISCO.08)) %>% 
  group_by(ISCO.title) %>% 
  summarise(Total = sum(ASECWT)) %>% 
  ungroup() %>% 
  top_n(.,n = 10,Total) %>% 
  arrange(desc(Total))
```
